DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-03 child_single_geo.Rmd
adds next steps
fixes plain text conditional text

```{r, eval=!has_both}
cat("This area does not have either known roads or known sidewalks or shoulders")
```

@@

>>>>

```{r, results = 'asis', eval=!has_roads}
cat("This area does not have either known roads.")
```

```{r, results = 'asis', eval=!has_sw_sh}
cat("This area does not have known sidewalks or shoulders.")
```

@@

```{r}
# next step
# take the comb data, get the distance for each segment
# combine that with this roads
# where no sw sh = 0
# determine if meets criteria
